---
title: "DRAFT - Covid Infections"
author: "MHCLG"
date: "`r format(Sys.Date()-1, '%d, %B, %Y')`"
output: html_document
---

# <span style="color: red;">Test Report Only</span>

This is a demonstration on designing choropleths in R using data from PHE.

Data from [Public health England](https://www.gov.uk/government/publications/covid-19-track-coronavirus-cases)

* **Data for map:** [UTLA cases table](https://www.arcgis.com/home/item.html?id=b684319181f94875a6879bbc833ca3a6) 


```{r knitr_init, echo=FALSE, cache=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      cache=FALSE,
                      message=FALSE,
                      warning=FALSE,
                      fig.width= 12,
                      fig.height= 12)
```

```{r include=FALSE}
# load packages
lapply(c( "tidyverse", "sf", "tmap", "lubridate","leaflet", "DT"), library, character.only = TRUE)

# download England Shape file
england_UA <- st_read("https://ons-inspire.esriuk.com/arcgis/rest/services/Administrative_Boundaries/Counties_and_Unitary_Authorities_April_2019_Boundaries_GB_BUC/MapServer/0/query?where=UPPER(ctyua19cd)%20like%20'%25E%25'&outFields=*&outSR=4326&f=geojson")

# Downlaod covid inections data
infections <- read.csv(url("http://www.arcgis.com/sharing/rest/content/items/b684319181f94875a6879bbc833ca3a6/data"),header = TRUE)

# load ONS codes 
ons_codes <- read.csv(file = "ons_codes.csv", header = TRUE)

# left join infectiosn data to the relvant location in England
england_cases <- left_join(x = england_UA,
                           y = infections[,c(1,3)],
                           by = c("ctyua19cd"="GSS_CD"))

# left join the region of each loaction in England
england_cases <- left_join(x = england_cases,
                           y = ons_codes[,c(2:3)],
                           by = c("ctyua19cd"="organisation_id"))

england_cases <- england_cases %>% mutate(roe = ifelse(test = england_cases$region_name == "London",yes = "London",no = "Rest of England"))

england_cases$name_abbr <- abbreviate(england_cases$ctyua19nm)

# Divide "Hackney & City of London" infection numbers into respective local authorities "Hackney" and "City of London"
# population of Hackney 280,000. population of CoL 10,000. 10/280 = 0.035

Hackney_CoL <- england_cases[which(england_cases$ctyua19nm == "Hackney"),][["TotalCases"]]

england_cases[which(england_cases$ctyua19nm == "Hackney"),][["TotalCases"]] <- round(Hackney_CoL * (1-0.035))
england_cases[which(england_cases$ctyua19nm == "City of London"),][["TotalCases"]] <- round(Hackney_CoL * 0.035)

```

## Total cases in England as of `r format(Sys.Date()-1, '%d, %B, %Y')`: **`r sum(england_cases[["TotalCases"]],na.rm = NA)`**

```{r warning= FALSE, message= FALSE,echo=FALSE,fig.align='center'}
england_cases %>% filter(roe != "London") %>%
  tm_shape() +
  tm_fill("TotalCases", style = "cont",  title = "Covid infections") +
  tm_borders(lwd = 1, lty = 1) +
  tm_text("name_abbr", size = 1, col = "black")+
  tm_style("col_blind")+
  tm_layout(frame = FALSE,legend.title.size=1,legend.text.size = 1, legend.position = c("left","centre"))

```

## Table: Confirmed cases in England (excluding London)

```{r warning= FALSE, message= FALSE,echo=FALSE,fig.align='center'}

ROE <- england_cases %>% filter(region_name != "London")
ROE_a <- ROE[[15]]
ROE_b <- as.character(ROE[[3]])
ROE_c <- ROE[[11]]

DT::datatable(cbind.data.frame(ROE_a,ROE_b,ROE_c) %>% rename(`Abbreviation` = ROE_a, `Unitary Authority` = ROE_b, `Total Cases` = ROE_c ))
```

## Total cases in London as of `r format(Sys.Date()-1, '%d, %B, %Y')`: **`r sum(england_cases[which(england_cases$roe == "London"),][["TotalCases"]],na.rm = NA)`**

```{r warning= FALSE, message= FALSE,echo=FALSE,fig.align='center'}
england_cases %>% filter(roe == "London") %>%
  tm_shape() +
  tm_fill("TotalCases", style = "cont",  title = "Covid infections") +
  tm_borders(lwd = 1, lty = 1) +
  tm_text("name_abbr", size = 1, col = "black")+
  tm_style("col_blind")+
  tm_layout(frame = FALSE,legend.title.size=1,legend.text.size = 1, legend.position = c("left","bottom"))

```

## Table: Confirmed cases in London

```{r warning= FALSE, message= FALSE,echo=FALSE,fig.align='center'}

London <- england_cases %>% filter(region_name== "London")
lon_a <- London[[15]]
lon_b <- as.character(London[[3]])
lon_c <- London[[11]]

DT::datatable(cbind.data.frame(lon_a,lon_b,lon_c) %>% rename(`Abbreviation` = lon_a, `Unitary Authority` = lon_b, `Total Cases` = lon_c ))
```



